### 2018-04-24 tex/paper.tex
Rename computeAll to stepBlock and other fixes

\item Observables are observed at a particular time and in a particular context. We assume that the recording and 
identification of each (instance of an) observation is provided by the infrastructure of the system. We provide a 
``little language'' for describing observations: \haskellinline{Observation}. 
\item
Similar properties are true for
\haskellinline{Money} amounts: their values are calculated depending on the inputs and state of execution of the 
contract, they can be deterministically established given the context, and they are described through a small 
``expression language''.
\item It is important to be aware that there may be different instances of contracts executed, and for each instance there will typically be different instances of observables (and commitments) observed and recorded.
\item The model manages the release of funds back to the committer when a cash commitment expires (see discussion of the \haskellinline{computeAll} function below).
\end{itemize}

@@

The function \haskellinline{step} is wrapped by the \haskellinline{stepAll} function, which calls \haskellinline{step} until it stops having any effects. For every block, the \haskellinline{computeAll} function is called. In addition to calling \haskellinline{stepAll}, \haskellinline{computeAll} will first enable expired cash commitments to be refunded and record any choices made at that step.

@@

If the cash is committed successfully and the timeout \haskellinline{t2} is reached, then it is impossible to further spend the committed cash, and any unspent funds can be reclaimed by participant \haskellinline{p}.
 This is performed by the \haskellinline{computeAll} function, as noted above.

@@

If the cash commitment with identifier \haskellinline{idCC} has expired, it becomes possible for the remaining funds to be redeemed by the committer; this can be done by the \haskellinline{computeAll} function processing the appropriate \haskellinline{Input}, and an \haskellinline{ExpiredCommitRedeemed} action will be produced.

>>>>

\item Observables are observed at a particular time and in a particular context. We assume that the recording and 
identification of each (instance of an) observation is provided by the infrastructure of the system. We provide a 
``little language'' for describing observations: \haskellinline{Observation}. 
\item
Similar properties are true for
\haskellinline{Money} amounts: their values are calculated depending on the inputs and state of execution of the 
contract, they can be deterministically established given the context, and they are described through a small 
``expression language''.
\item It is important to be aware that there may be different instances of contracts executed, and for each instance there will typically be different instances of observables (and commitments) observed and recorded.
\item The model manages the release of funds back to the committer when a cash commitment expires (see discussion of the \haskellinline{stepBlock} function below).
\end{itemize}

@@

The function \haskellinline{step} is wrapped by the \haskellinline{stepAll} function, which calls \haskellinline{step} until it stops having any effects. For every block, the \haskellinline{stepBlock} function is called. In addition to calling \haskellinline{stepAll}, \haskellinline{stepBlock} will first enable expired cash commitments to be refunded and record any choices made at that step.

@@

If the cash is committed successfully and the timeout \haskellinline{t2} is reached, then it is impossible to further spend the committed cash, and any unspent funds can be reclaimed by participant \haskellinline{p}.
 This is performed by the \haskellinline{stepBlock} function, as noted above.

@@

If the cash commitment with identifier \haskellinline{idCC} has expired, it becomes possible for the remaining funds to be redeemed by the committer; this can be done by the \haskellinline{stepBlock} function processing the appropriate \haskellinline{Input}, and an \haskellinline{ExpiredCommitRedeemed} action will be produced.
